%!TEX root = cv.tex

\vbox{%
\newsection{Communications \& Media}{comms}

\subsection*{Websites}
\label{sec:web}
\vspace{-0.1in}
}

\begin{description}[itemsep=6pt]
  \item \href{https://www.ninds.nih.gov/about-ninds/who-we-are/staff-directory/joseph-monaco}
    {``\itemtitle{Joseph Monaco, Ph.D. -- Scientific
      Program Manager, NIH BRAIN Initiative}.'' Website.
    \aurl{https://www.ninds.nih.gov/about-ninds/who-we-are/staff-directory/joseph-monaco}}
  \item \href{https://jdmonaco.com/}
    {``\itemtitle{Briefly Balanced: Complexity through neural dynamics and physical constraints}.'' Website. \aurl{https://jdmonaco.com/}}
  \item \href{https://jdmonaco.com/google-scholar}
    {\itemtitle{Google Scholar}. Website. \aurl{https://scholar.google.com/citations?hl=en\& user=gceOLZEAAAAJ\&view\_op=list\_works\&sortby=pubdate}}
  \item \href{https://orcid.org/0000-0003-0792-8322}
    {\itemtitle{ORCID Profile}. Website. \aurl{https://orcid.org/0000-0003-0792-8322}}
  \item \href{https://www.linkedin.com/in/jdmonaco/}
    {\itemtitle{LinkedIn Profile}. Website. \aurl{https://www.linkedin.com/in/jdmonaco/}}
  \item \href{https://www.ncbi.nlm.nih.gov/pubmed/?term=monaco_jd+OR+(monaco_j+AND+muzzio_ia)}
    {\itemtitle{PubMed Listing}. Website.
    \aurl{https://www.ncbi.nlm.nih.gov/pubmed/?term=monaco\_jd}}
  \item \href{https://github.com/jdmonaco}
    {\itemtitle{GitHub Overview}. Website. \aurl{https://github.com/jdmonaco}}
\end{description}

\vbox{%
\subsection*{Media \& Press Releases}
\label{sec:media}
\vspace{-0.1in}
}

\begin{description}[itemsep=6pt]
  \item \href{https://www.thetransmitter.org/brain-inspired/grace-hwang-and-joe-monaco-discuss-the-future-of-neuroai/} 
    {``\itemtitle{Brain Inspired 200: Grace Hwang and Joe Monaco discuss
      the future of NeuroAI}.'' Brain-Inspired Podcast (The Transmitter).
      December 4, 2024. \aurl{https://www.thetransmitter.org/brain-inspired/
    grace-hwang-and-joe-monaco-discuss-the-future-of-neuroai/}}
  \item \href{https://www.jhuapl.edu/NewsStory/220919-stem-teaching-tool-recognized-ieee-isec-2022}{
      ``\itemtitle{Novel Teaching Tool Earns Hopkins Collaborators
      International Conference Honors}.'' JHUAPL Press Office. Sept 19, 2022.
      \aurl{https://www.jhuapl.edu/NewsStory/220919-stem-teaching-tool-
    recognized-ieee-isec-2022}}
  \item \href{https://kavlijhu.org/news/32} {``\itemtitle{Can
        robotic swarms navigate using learning rules devised for brain
      dynamics?}'' JHU/Kavli Neuroscience Discovery Insitute. May 3, 2020.
    \aurl{https://kavlijhu.org/news/32}}
  \item \href{https://www.youtube.com/watch?v=ic4zEgVMSsA}
    {``\itemtitle{Swarmalators}.'' JHUAPL Press Office. May 9, 2019.
    \aurl{https://www.youtube.com/watch?v=ic4zEgVMSsA}}
  \item \href{https://hub.jhu.edu/2018/10/02/brain-robot-swarms-study/}
    {``\itemtitle{What do animal brains have in common with swarms of robots?
      Maybe more than you think}.'' Geoff Brown/JHU Office of Communications. Oct 2,
    2018. \aurl{https://hub.jhu.edu/2018/10/02/
  brain-robot-swarms-study/}}
  \item \href{https://www.jhuapl.edu/PressRelease/181001}
    {``\itemtitle{Do Robot Swarms Work Like Brains?}'' JHUAPL Press Office. October 1, 2018.
    \aurl{https://www.jhuapl.edu/PressRelease/181001}}
  \item \href{https://hub.jhu.edu/2014/04/14/memory-brain-place-cells/}
    {``\itemtitle{Where does a memory begin? Johns Hopkins neuroscientists think they
      know}.'' Latarsha Gatlin/JHU Office of Communications. April 14, 2014.
    \aurl{https://hub.jhu.edu/2014/04/14/memory-brain-place-cells/}}
  \item \href{https://www.youtube.com/watch?v=Jm8OiLJqKJQ}
    {``\itemtitle{Johns Hopkins Researchers Probe Mysteries of
      the Brain}.'' JHU Office of Communications. April 14, 2014.
    \aurl{https://www.youtube.com/watch?v=Jm8OiLJqKJQ}}
\end{description}

