%! TEX program = xelatex
%
% Curriculum vitae for Joseph D. Monaco
%
\documentclass[10pt]{article}

\usepackage{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage[hidelinks,xetex]{hyperref}
\usepackage{multirow}
\usepackage{sectsty}
\usepackage{enumitem}
\usepackage{tabu}
\usepackage{longtable}
\usepackage{soul}
\usepackage{fontspec}

% Page geometry formatting
\raggedbottom
\raggedright
\textheight=9in
\setlength{\tabcolsep}{0in}
\addtolength{\footskip}{.3in}
\addtolength{\voffset}{-.4in}
\addtolength{\textheight}{.4in}
\addtolength{\hoffset}{-.25in}
\addtolength{\textwidth}{.2in}

% Define colors
\definecolor{hopkinsblue}{RGB}{0,48,130}
\definecolor{lightblue}{rgb}{.88,.92,.97}
\definecolor{lightgold}{rgb}{1,.80,0}
\definecolor{lightred}{rgb}{1,.3,.2}
\definecolor{lightgray}{rgb}{.80,.80,.80}
\definecolor{dimgray}{rgb}{.50,.50,.50}
\definecolor{darkgray}{rgb}{.30,.30,.30}

% Set up highlighting and underlining
\sethlcolor{lightblue}
\setul{0.13ex}{}

% Choose font package
\setmainfont[Ligatures=TeX]{Helvetica Neue LT Std} 

% Section section* formatting
\sectionfont{\large\color{hopkinsblue}\bfseries}
\subsectionfont{\vspace{-1ex}\color{hopkinsblue}\normalsize\bfseries}

% Formatting macros
\newcommand{\itemtitle}[1]{{\color{hopkinsblue}\ul{#1}}}
\newcommand{\unpubtitle}[1]{{\color{hopkinsblue} #1}}
\newcommand{\itemnote}[1]{
  \begin{description}
    \item[$\rightarrow$] \hspace{.09in}{\color{darkgray}\it #1}
  \end{description}
}
\newcommand{\joehl}[1]{\hl{\textbf{#1}}}
\newcommand{\doi}[1]{{\color{darkgray}doi:}~{\color{dimgray}\texttt{#1}}}
\newcommand{\arxiv}[1]{\emph{ArXiv Preprint}.
  {\color{darkgray}arxiv:}{\color{dimgray}\texttt{#1}}}
\newcommand{\arxivlink}[1]{\href{https://arxiv.org/abs/#1}
  {{\color{darkgray}arxiv:}~{\color{dimgray}\texttt{#1}}}}
\newcommand{\biorxivlink}[1]{\href{https://dx.doi.org/#1}
  {{\color{darkgray}biorxiv:}~{\color{dimgray}\texttt{#1}}}}
\newcommand{\aurl}[1]{{\color{dimgray}\texttt{#1}}}
\newcommand{\researchnote}[1]{
  \begin{description}
    \item[] {\hspace{2.2ex}\color{darkgray} #1}
  \end{description}
}
\newcommand{\researchactivity}[4]{
  \begin{minipage}[t]{\textwidth}
    \begin{tabular}{@{\hspace{2ex}}l>{\raggedright\arraybackslash}p{.8\textwidth}}
      \makebox[1.2in][l]{#1} & \textbf{#2:}
      ``\unpubtitle{#3}'' 
    \end{tabular}
  \researchnote{\hspace{1ex} #4}
  \end{minipage}
  \medbreak
}
\newcommand{\whitepaper}[4]{
  \begin{minipage}[t]{\textwidth}
    \begin{tabular}{@{\hspace{2ex}}l>{\raggedright\arraybackslash}p{.8\textwidth}}
      \makebox[1.2in][l]{#1} & \textbf{White Paper:} #2.
      ``\unpubtitle{#3}'' 
    \end{tabular}
  \researchnote{\hspace{1ex} #4}
  \end{minipage}
  \medbreak
}
\newcommand{\lefttabline}[3]{\hspace{2ex}\makebox[#1][l]{#2} #3\\}

% PDF document info and setup
\hypersetup{
  baseurl=https://jdmonaco.com/cv-monaco.pdf,
  pdftitle=Curriculum Vitae for Joseph D. Monaco,
  pdfauthor=Joseph D. Monaco,
  pdfdisplaydoctitle=true,
  pdfpagemode=UseThumbs,
  pdfstartview=FitV,
  pdfpagelayout=TwoColumnLeft,
  pdftoolbar=false,
  pdfwindowui=false,
  pdfcenterwindow=true,
}

% "See section ..." macro
\newcommand{\see}[1]{[\textcolor{hopkinsblue}{p.\pageref{sec:#1}}]}
\newcommand{\cfonly}[1]{\textcolor{hopkinsblue}{\emph{\nameref{sec:#1}} on p.\pageref{sec:#1}}}
\newcommand{\cf}[1]{\textcolor{hopkinsblue}{See \emph{\nameref{sec:#1}} on p.\pageref{sec:#1}}}
\newcommand{\cfcf}[2]{\textcolor{hopkinsblue}{See \emph{\nameref{sec:#1}} on
  p.\pageref{sec:#1} and \emph{\nameref{sec:#2}} on p.\pageref{sec:#2}}}

% Typesetting
\setlength{\parskip}{0.75em}
\setlist{nosep}

% Section-heading macros
\newcommand{\newsection}[2]{%
  \section*{#1}
  \vspace{-.1in}
  \hrule
  \vspace{.2in}
  \label{sec:#2}
}
\newcommand{\newsubsection}[2]{%
  \subsection*{#1}
  \vspace{-.08in}
  \hrule
  \vspace{.1in}
  \label{sec:#2}
}

\begin{document}

\begin{center}
  \textbf{\LARGE\color{hopkinsblue} Joseph D. Monaco, Ph.D.} \\[0.1in]
  Baltimore, Maryland, United States \\
  \href{mailto:joseph.monaco@nih.gov}{\color{hopkinsblue}\texttt{joseph.monaco@nih.gov}} •
  \href{tel:16674067398}{\color{hopkinsblue}\texttt{667.406.7398}} \\
  \vspace{.1in}
\end{center}
%\thispagestyle{empty}

\vspace{-0.1in}
\newsection{Health Scientist Administrator (HSA): Duties, Requirements, \& Qualifications}{duties}
\vspace{-0.1in}

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Manage program workloads and ensure timely completion of project
milestones.}
\end{itemize}

Since January 2023 (2 years), in my current role supporting the NIH BRAIN
Initiative, I have managed multiple complex workstreams including policy
implementation, workshop organization, strategic planning, and cross-team
coordination. \cf{jobobd}. A key example is my leadership of the BRAIN
NeuroAI Workshop planning process in 2024 (1 year), where I successfully
coordinated internal NIH and external scientific planning committees, secured
authorizations, and executed a major two-day event despite budget constraints
and logistical obstacles, resulting in participation from nearly 2,000 attendees
(200 in-person) from 48 countries.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Direct research activities to maintain focus on programmatic
goals.}
\end{itemize}

Since January 2023 (2 years), I have provided strategic direction for multiple
BRAIN research programs~\see{jobobd}, ensuring alignment with BRAIN Initiative
priorities in data science, theory, and computational modeling. For example, I
led development of new data sharing workflows that improved efficiency while
maintaining rigorous standards. In addition, I am currently working to guide the
post-workshop NeuroAI strategic planning porcess across BRAIN Teams and working
groups to establish research priorities advancing BRAIN's mission over the next
decade.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Coordinate with leadership to obtain and allocate necessary
program resources.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I regularly
advise the BRAIN Director on scientific and technological priorities, supporting
decision-making through analysis and recommendations that guide decisions around
program resource allocations. For example, my implementation strategy for
BRAIN's data management and sharing policy avoided unnecessary expenditures for
up-front development costs which may have otherwise exceeded \$500,000, while
still achieving policy objectives. In 2024, I successfully secured resources for
the BRAIN NeuroAI Workshop held in November despite FY24 budget constraints.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Review grant applications and analyze proposals from program
perspective.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I have served as
a subject matter expert (SME) for multiple BRAIN Teams, providing scientific
and programmatic review of grant applications for funding opportunities related
to computational neuroscience, theoretical neuroscience, systems neuroscience,
neuromorphic computing, software tools, and data science. I developed reference
language for new funding opportunities (NOFOs) developed by BRAIN Teams and
established improved workflows for program staff to evaluate research proposals
and data management and sharing (DMS) plans. In 2024, I also contributed ad-hoc
reviews of funding applications for the Air Force Office of Sponsored Research
(AFOSR). \cf{service}.

In 2021 and 2022 (2 years), before joining the NIH, I contributed to the
development of a competitive National Science Foundation (NSF) EFRI program
topic, served on several review panels for the successfully adopted EFRI topic,
and provided ad-hoc reviews for the NSF CAREER program. \cf{programsvc}.

Several times from 2016 to 2024 (4 years total), I provided review service
for scientific conferences. In 2024, I contributed ad-hoc reviews of paper
submissions for the Neuro-Inspired Computational Elements (NICE) Conference.
From 2016 to 2021, I served three times on the Review Committee for the
Computational Systems Neuroscience (Cosyne) conference. \cf{confsvc}.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Guide applicants and grantees on program requirements, policies,
and opportunities.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I have
provided guidance to investigators on grant applications, data sharing policy
expectations and requirements, and program priorities across multiple BRAIN
portfolios. Additionally, I created and implemented new standard operating
procedures that streamlined communications between program staff and applicants,
reducing overall burden while maintaining high standards for maximizing the
scientific impact of NIH and BRAIN data sharing.

From 2018 to 2022 (5 years), before joining the NIH, I met with various
program directors from the Navy (Office of Naval Research) and the NSF (ENG,
CISE) to discuss how to maximize program relevance of applications that I was
preparing. From this experience, I wrote or co-wrote and submitted a number of
whitepapers and grant applications at various levels of project size and budget.
\cf{res}. Through these discussions and the subsequent development and
programmatic review of my submitted applications, I gained substantial and
varied knowledge of the role of program officers in guiding investigators as
they develop applications to align with mission criteria and program priorities.


\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Develop and manage grants and cooperative agreements supporting
program mission and objectives.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I have worked
closely with multiple BRAIN Teams to support development and coordination of
cooperative agreements and research awards, providing SME programmatic reviews
during pre- and post-award phases. I have served as a resource for program
teams to ensure alignment of milestones with the DMS policy expectations of
NIH and the BRAIN Initiative. In addition, my contributions include providing
program staff on data sharing requirements for new awards, participating in
BRAIN consortium network meetings like BICAN and CONNECTS, and helping evaluate
milestone progress for complex cooperative agreements to verify continued
alignment with BRAIN objectives.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Organize scientific workshops and conferences to advance program goals.}
\end{itemize}

Since January 2023 (2 years), in my current role in the Office of the BRAIN
Director (OBD)~\see{jobobd}, I have demonstrated extensive experience planning
and executing scientific meetings at multiple scales, from co-organizing
focused sessions to leading major workshops. I co-organized the ``Embodied
NeuroAI'' specialty session at the recent BRAIN Initiative Conference (June
2024)~\see{natltalks} and a panel discussion on the future sustainability of the
BRAIN data ecosystem for the INCF Assembly (September 2024)~\see{intltalks}. My
leadership of the BRAIN NeuroAI Workshop planning efforts showcased my ability
to manage complex engagements, including coordinating with logistics contractors
for attendee registration, 508c compliance, venue arrangements, managing hybrid
participation platforms, and organizing an early-career poster competition to
ensure a successful workshop.

From 2019 to 2020 (1 year), prior to joining the NIH, I co-organized a
scientific symposium that took place (virtually) at the 2020 BRAIN Initiative
Investigators Meeting~\see{symposium}. This symposium brought together a panel
of 5 leading researchers, including me, to explore key relationships between
machine learning and dynamical systems neuroscience that are critical to
advancing BRAIN's program objectives relating to theory, modeling, and data
analysis.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Visit universities and attend conferences to conduct program
outreach to diverse audiences.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I have
regularly represented the NIH BRAIN Initiative at major scientific
conferences and workshops, including recent international presentations at
NeurIPS, SfN, INCF Assembly, IEEE/ACM ICONS, and the Telluride Neuromorphic
Workshop~\see{intltalks}. My outreach activities have built crucial
relationships with academic, commercial, and government partners, exemplified by
my coordination with the Allen Institute, MIT, and other major BRAIN-supported
research centers.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Communicate complex scientific topics effectively to a variety of
national audiences.}
\end{itemize}

Since 2010 (14 years), across my career, I have had extensive experience
communicating scientific concepts through diverse channels at national
and international venues, ranging from delivering research talks at
major conferences to participating in policy-focused panel discussions.
\cfcf{talks}{comms}. Recent examples include recording an interview about
theoretical neuroscience and the BRAIN NeuroAI Workshop for the popular
Brain-Inspired Podcast~\see{media}, drafting blog posts for the BRAIN Blog,
developing internal communications and reports about BRAIN Initiative efforts
and priorities, and leading technical and policy-oriented discussions
across scientific domains including neuroscience, AI, informatics, data
science, and neuromorphic computing. 

Since 2010 (14 years), I delivered numerous scientific seminars and invited
lectures~\see{talks} at top research universities---e.g., the University
of Minnesota in 2020 and the University of Toronto in 2022---and public
organizations---e.g., the Neuromatch Conference series from 2020--2021 and
the Air Force Research Laboratory (AFRL) in 2022 and 2023---to communicate
scientific findings and perspectives from my research.

From 2018 to 2021 (4 years), prior to joining the NIH, I collaborated
extensively with the Johns Hopkins University Applied Physics Laboratory
(JHUAPL) on efforts to develop federal funding applications, manage the
resulting awards, and execute the projects by leading a cross-divisional team
to conduct research, publish findings, disseminate outreach materials, and
contribute to educational components. \cfcf{res}{eduprogram}.

My ability to effectively communicate complex topics to varied audiences is
demonstrated through a long history of invited presentations and successful
collaborations at universities, research centers, workshops, conferences,
panels, podcasts, and seminars.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Develop policies advancing scientific programs of national
importance related to health.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I have led
development and implementation of policies that advance BRAIN's mission,
including data management and sharing requirements that promote open science.
I currently guide strategic planning efforts to establish BRAIN as a leader in
NeuroAI research, working to develop partnerships with other agencies to shape
priorities and policies that will guide the future of neuroscience research and
neurotechnologies critical to brain health.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Support program leadership by serving as liaison to teams of
extramural program officers and staff.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I have served
as Office of the BRAIN Director liaison to multiple BRAIN Teams and working
groups, including the BRAIN NeuroAI Working Group which I formed in late
2023 and for which I have since served as co-lead. As a team liaison, I have
coordinated activities between program staff, project scientists, intramural
consultants, and leadership, including division directors and branch chiefs
across multiple BRAIN-participating ICs. My accomplishments in developing
DMS policy implementations across BRAIN programs and portfolios demonstrate
my ability to orchestrate complex workflows across diverse roles, resulting
in improved efficiency and reduced burden. 

Since January 2023 (2 years), in addition, I have served as a BRAIN liaison
or representative on trans-NIH working groups (for example, consciousness
research), special interest groups (for example, AI), program (for example,
the NIH Common Fund, including the recently launched Complement-ARIE program),
and the NSF--NIH Smart and Connected Health (SCH) program's cofunding
office team. My contributions to these trans-NIH initiatives include SME
review, implementation planning, concept development, and serving as the
scientific/research contact of record on published NSF and NIH funding
solicitations.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Build working relationships with leading scientists by engaging
through conferences and outreach.}
\end{itemize}

In my current role~\see{jobobd}, I have maintained extensive engagement with
the scientific community through conference participation, site visits, and
other investigator meetings. My leadership of the NeuroAI workshop planning
committee exemplifies my ability to build productive relationships with leading
researchers, resulting in successful coordination across academic, government,
and private sector partners.


%%% Requirements & Qualifications %%%

\newsection{Requirements \& Qualifications}{basicreqs}

\subsection*{Conditions of Employment}

\begin{itemize}
  \item \emph{I am a U.S. citizen.}
  \item \emph{I will submit all required documents.}
  \item \emph{All qualifications are already met and will be met by the closing date.}
  \item \emph{I registered with the Selective Service at the appropriate age.}
  \item \emph{Transcripts are attached in fulfillment of the education requirement.}
  \item \emph{I am able to perform the essential duties of the position.}
\end{itemize}

\subsection*{Basic Education Requirements}

I hold a Ph.D. (2009), M.Phil. (2008), and M.A. (2006) in Neurobiology \&
Behavior from Columbia University, where I trained at the Center for Theoretical
Neuroscience. I completed my initial graduate coursework in the Neuroscience
Program at Brandeis University's Volen Center for Complex Systems before
continuing my doctoral research at Columbia. Prior to Brandeis, I earned dual
B.A. degrees in Mathematics and Cognitive Science with a Minor in Philosophy
from the University of Virginia (2003), where I was an Echols Scholar. My
graduate training focused on computational and theoretical approaches to
understanding brain function, directly aligning with the position's requirement
for advanced study in health sciences and allied fields. \cf{education} for
additional details.

\subsection*{Requirements for Applicants at the GS-15 Grade Level}
\vspace{-.1in}
\hrule
\vspace{.1in}
\subsubsection*{A. Direct/Independent Research Qualifying Experience}

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Managed diverse scientific health-related research programs with
national and international impact.}
\end{itemize}

Since January 2023 (2 years), in my current role supporting the NIH BRAIN
Director, I have supported and contributed to multiple high-impact research
programs focused on whole-brain cell atlasing, circuits/systems neuroscience,
artificial intelligence, ccomputational modeling, theory, open data standards,
and reproducible analytics workflows. \cf{jobobd}. I worked across BRAIN Teams
and led initiatives spanning multiple NIH institutes, including managing the
launch of a new team focused on data sharing and informatics programs, creating
and leading a new working group focused on new opportunities at the intersection
of neuroscience and AI (``NeuroAI''), and leading the planning efforts for the
BRAIN NeuroAI Workshop that took place on November 12 and 13, 2024. The BRAIN
NeuroAI Workshop was a 2-day hybrid event that was attended in-person (200)
or virtually (1,749) by almost 2,000 participants from 48 countries. Through
these efforts, I built collaborative networks across key academic researchers,
commercial partners from startups to the top tech companies, and government
agencies (NIH, ARPA-H, NSF, DOE, DOD), demonstrating my ability to manage
diverse research programs, coordinate crucial outreach, and build the key
relationships needed to enable transformative national and international impact.

From 2019 to 2022 (3 years), as Research Associate faculty in the Johns
Hopkins University School of Medicine (JHU/SOM)~\see{job1}, I served as
principal investigator (or co-PI) of multiple federal grant-awarded projects
that I initiated independently, including a NIH/NINDS R03 award and a NSF/NCS
FOUNDATIONS award, part of the NSF's BRAIN Initiative portfolio. In these
projects, I build computational tools and co-developed cross-disciplinary
mathematical frameworks to address physiological mechanisms underlying
cognitive mapping and episodic memory formation, theoretical advances in
the understanding of neural oscillations as a basis of self-organizing
spatiotemporal activity patterns in brains, and established approaches to
translating theoretical advances to early-stage technological applications,
including multi-agent robotic metacontroller models. \cf{funding}. During that
time, I also independently initiated new collaborations and developed several
other research projects, leading to an inter-disciplinary NSF application in 2020
and an internal JHU application in 2022. \cf{res}.

To manage the above projects (2019--2022, 3 years), I developed protocols
including reference computational models, conducted data analyses, supervised
and mentored graduate students and junior staff~\see{mentoring}, and
administered the grants by coordinating with JHU administrators, integrating and
writing progress reports for funding agencies, applying for no-cost extensions,
and depositing published papers in agency-hosted archives such as the NSF Public
Access Repository. At least six (6) peer-reviewed publications resulted from
these collaborative, cross-divisional projects. \cf{hadzicpub}.
%
%\begin{quote}
  %• Hadzic, Hwang, Zhang, Schultz, Monaco (2022) \emph{Array}. \\
  %• Buckley, Monaco, Schultz, Chalmers, Hadzic, Zhang (2022) In: IEEE
  %Integrated STEM Education Conference (ISEC'22). \\
  %• Schultz, Villafañe-Delgado, Reilly, Saksena, Hwang (2022) In: Emergent
  %Behavior in System of Systems Engineering. \\
  %• Hwang, Schultz, Monaco, Zhang (2021) \emph{JHUAPL Technical Digest}. \\ 
  %• Monaco, Hwang, Schultz, Zhang (2020) \emph{Biological Cybernetics}. \\ 
  %• Monaco, Hwang, Schultz, Zhang (2019) In: International Society for
  %Photonics (SPIE'19). \\
%\end{quote}
%%
%The first author (Hadzic) of the first paper above was a JHUAPL junior staff
%member whom I mentored~\see{mentoring}. \cf{pubs} for complete publication
%details.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Developed strategic plans for resource allocation across competing
research programs.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I have developed
new priority areas for strategic planning initiatives within the BRAIN
Initiative, including a new vision for a sustainable BRAIN data ecosystem.
At the same time, I have implemented and refined the recently established
data management and sharing (DMS) policies that mandate research data sharing
across the NIH and BRAIN. My DMS workflows have improved program efficiency
while reducing costs. I advised the BRAIN Director on resource allocation
decisions across multiple research programs and helped establish criteria for
evaluating competing proposals. My recommendations on implementation strategies
avoided unnecessary expenditures exceeding \$500,000 while maintaining program
effectiveness.

Since February 2024 (1 year), as founder and co-lead of the BRAIN NeuroAI
Working Group~\see{jobobd}, I organized a substantial strategic planning effort
to identify innovative NeuroAI opportunities for the NIH BRAIN Initiative.
This effort was highly integrated with planning and pre-coordination of the
BRAIN NeuroAI Workshop that I co-organized with my working group in November
2024. The NeuroAI thrust is one of a small number of strategic priority areas
competitively selected by the BRAIN Director in Summer 2024 for continued
scoping and implementation. Since the workshop, I have led the integration,
synthesis, and development of the NeuroAI concept in collaboration with BRAIN
programs and teams, communicated updates to leadership, and developed critical
planning documents to harmonize workshop inputs reflecting community interest
with BRAIN mission-relevance and portfolio synergies.

From 2009 to 2022 (13 years), I was a Research Associate faculty
(3~years) developing and administering an independent cross-divisional
and interdisciplinary research program~\see{job1}; a JHU/SOM Postdoctoral
Fellow (5~years) performing preclinical health-related neuroscience
research~\see{job2}; and a JHU Postdoctoral Fellow (5~years) conducting
behavioral neuroscience and theory-driven computational modeling
research~\see{job3}. In these academic roles, I gained broad experience
developing skills for strategic planning, resource allocation, and project
management in funding-constrained, grant-driven research environments and varied
scientific and administrative contexts.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Achieved scientific distinction through research accomplishments
    and professional society membership.}
\end{itemize}

Since obtaining my Ph.D. in 2009 (15 years), I have continually worked to
establish scientific distinction through research contributions in theoretical
and computational neuroscience and adjacent fields, culminating in publications
in prestigious journals including Nature Neuroscience, Cell, PLOS Computational
Biology, Biological Cybernetics, and the Journal of Neuroscience. My work
on spatial cognition, neural computation, and theoretical neuroscience has
been recognized through invited presentations at major institutions and
conferences. Recent invitations to speak at high-profile conferences and venues
including NeurIPS, INCF Assembly, Society for Neuroscience, the BRAIN Initiative
Neuroethics Working Group (NEWG), and the Open Data in Neuroscience (ODIN)
symposium reflect my growing scientific impact. \cfcf{journalpubs}{talks}.

From 2016 to 2018 (3 years), as a JHU/SOM Postdoctoral Fellow~\see{job2}, I
independently initiated collaborations and research projects resulting in an
internal JHU Science of Learning Institute award~\see{funding}
and the development and submission of two external (NIH and NSF) applications
that were awarded starting FY19. In that time, I additionally conceived and
coordinated a large collaborative project proposal among 8~labs across JHU
that was selectively funded by DARPA/BTO and targeted noninvasive stimulation
of neuroplasticity for health-related interventions and augmentation.
\cfcf{funding}{res}

From 2009 to 2014 (5 years), as a JHU Mind/Brain Institute (JHU/MBI) Postdoctoral
Fellow~\see{job3}, I conducted a statistical modeling study of neurobehavioral
datasets and developed protocols for behavioral quantification of rats
performing spatial navigation experiments. My study provided the first evidence
for mammalian long-term memory formation tied to individual behaviors (i.e.,
lateral head-scanning movements). In collaboration with my postdoctoral lab, I
interpreted and published my findings in high-impact journals, including Nature
Neuroscience and Current Biology. \cf{journalpubs}
%
%\begin{quote}
  %• Monaco, Rao, Roth, Knierim (2014) \emph{Nature Neuroscience}. \\ 
  %• Wang, Monaco, Knierim (2020) \emph{Current Biology}. \\ 
%\end{quote}
%
%The first author (Wang) of the second paper above was a graduate student whom
%I mentored~\see{mentoring}. My head-scanning study provided the basis for my
%2010 application and 2011 resubmission of a NIH NRSA Postdoctoral Fellowship
%(F32)~\see{nrsa}, as guided by discussions that I initiated with NINDS PO Jim
%Gnadt. \cf{pubs} for complete details.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Represented organizations on committees evaluating scientific
research priorities.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I have served as
an extramural SME for programmatic review on multiple BRAIN Teams evaluating
research funding applications across BRAIN programs and portfolios. I have led
working groups focused on artificial intelligence, neuromorphic engineering,
and theoretical neuroscience, culminating in organizing a major workshop that
brought together diverse research communities and stakeholders across multiple
sectors of science, technology, and health to shape future research priorities
for NeuroAI. In addition, I served on the BRAIN Initiative Conference Program
Committee in 2024 and I regularly participate in trans-NIH working groups and
represent BRAIN on program/policy implementation working groups, including for
the NIH Common Fund Complement-ARIE program and for NSF--NIH Smart Health,
for which I am the scientific/research contact of record on the published
solicitations.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Published research findings in high-impact scientific journals.}
\end{itemize}

From 2007 to 2024, I have published 14 peer-reviewed papers in leading
journals spanning computational neuroscience, cognitive science, biology, and
artificial intelligence. My work includes seminal contributions in Nature
Neuroscience, Cell, Current Biology, and PLOS Computational Biology. Recent
publications focus on theoretical advances in neurodynamical computing, Bayesian
optimization for neural control, and perspectives on computational modeling in
neurorehabilitation, demonstrating continued scientific productivity and impact.
\cf{journalpubs}.

%From 2014 to 2016, I conducted a computational modeling and neural data analysis
%study in which I developed neural coding protocols, documented my findings, and
%interpreted the results in a substantial original research article integrating
%multiple convergent methodological approaches that I carried from preprint to
%publication in a high-impact journal:
%%
%\begin{quote}
  %• Monaco, De Guzman, Blair, Zhang (2019) \emph{PLOS Computational Biology}. \\ 
  %• Monaco, Blair, Zhang (2017) \emph{bioRxiv}. \\ 
%\end{quote}
%%
%\cf{pubs} for complete publication details. 

\subsubsection*{B. Research Administration/Extramural Qualifying Experience}

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Established evaluation standards for planning and reviewing
scientific research projects.}
\end{itemize}

Since January 2023 (2 years), I have developed and implemented standard
operating procedures for evaluating data management and sharing (DMS) plans
across the BRAIN Initiative. I created reference language for new funding
opportunity announcements and established workflows for program staff to review
DMS plans submitted with research proposals. My improvements to DMS evaluation
and review processes have streamlined communications between Office of the
BRAIN Director, Program Staff, applicants, and Grants Management, reducing
administrative burden while enhancing the value of rigorous DMS evaluation
standards. \cf{jobobd}.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Assessed emerging research trends to advance organizational
missions and program objectives.}
\end{itemize}

Since January 2023 (2 years), I have led efforts to evaluate and shape the
emerging field of NeuroAI within the BRAIN Initiative. Through organizing a
major workshop attended by nearly 2000 participants, I facilitated critical
discussions about integrating artificial intelligence approaches with
neuroscience research. I advised BRAIN leadership on strategic opportunities
in computational modeling, neuromorphic computing, and data-driven research,
helping establish programmatic priorities that advance NIH's mission to improve
human health through scientific discovery. \cf{jobobd}.

Prior to joining the NIH, my 2019 publication (Monaco et al., 2019, PLOS
Comput Biol)~\see{pubs} laid the theoretical and experimental groundwork
for establishing my collaboration with JHUAPL, the resultant NSF-awarded
project~\see{funding}, my co-organization of and participation in a
well-attended NIH BRAIN Investigators symposium in 2020~\see{symposium}, and
my interactions with NSF program directors that led to my initial extramural
contributions to the programmatic development and review of a competitively
funded NSF EFRI program topic (\href{https://www.nsf.gov/awardsearch/advancedSearchResult?PIId=&PIFirstName=&PILastName=&PIOrganization=&PIState=&PIZip=&PICountry=&ProgOrganization=07040000&ProgEleCode=7633&BooleanElement=All&ProgRefCode=&BooleanRef=All&Program=&ProgOfficer=&Keyword=BRAID&AwardNumberOperator=&AwardAmount=&AwardInstrument=&ActiveAwards=true&OriginalAwardDateOperator=&StartDateOperator=&ExpDateOperator=}{\unpubtitle{BRAID}}) 
with \$30M total awarded from 2020 to 2022. \cf{programsvc}.

\begin{itemize}
  \color{hopkinsblue}
  \item \emph{Coordinated multi-agency initiatives to identify and address
research program needs.}
\end{itemize}

Since January 2023 (2 years), in my current role~\see{jobobd}, I have built
collaborative relationships across multiple federal agencies including NSF,
DOE, ARPA-H, and DOD to advance shared research priorities. I initiated the
co-funding participation of the NIH BRAIN Initiative in the joint NSF--NIH Smart
and Connected Health (SCH) program. Moreover, I contributed to internal program
discussions regarding BRAIN co-funding priorities and implementation of the
NSF--NIH CRCNS (Collaborative Research in Computational Neuroscience) Program.

I leveraged this experience during planning for the 2024 BRAIN NeuroAI Workshop
to both initiate and build upon potential cross-agency and cross-sector (private
foundations, investors, and tech companies) partnerships. I am currently leading
post-workshop coordination efforts to coaelesce NeuroAI initiatives across
government agencies and other stakeholders, developing shared interest to lay
the groundwork for for potential joint research investments. \cf{jobobd}.

%\subsection*{Requirements for the GS-13 Level}

%\begin{itemize}
  %\item \emph{Managed significant independent research projects}.
    %\itemnote{\cfcf{basicreqs}{res}.}
  %\item \emph{Supervised graduate researchers and junior technical staff}.
    %\itemnote{\cf{mentoring}.}
  %\item \emph{Published in refereed journals}. \itemnote{\cf{pubs}.}
  %\item \emph{Presented published work to scientific organizations}.
    %\itemnote{\cfcf{talks}{presentations}.}
  %\item \emph{Served as a reviewer on peer-review panels and journals}.
    %\itemnote{\cfcf{service}{programsvc}.}
  %\item \emph{Held the position of Assistant or Associate Professor or
      %equivalent}. \itemnote{\cf{cv} and the above-linked sections to assess the
        %depth and breadth of my academic credentials. Note that, as of 2019, the
        %JHU/SOM Provost for Postdoctoral Affairs evaluated my C.V. as being equivalent
        %to a mid-tenure-track Assistant Professor, i.e., approximately 3 years from
        %tenure and promotion to Associate Professor rank. Given my experience accrued
        %in the three years since that evaluation, I would estimate that my position as
        %of 2022 should be fairly judged as equivalent to a recently tenured Associate
      %Professor.}
  %\end{itemize}

%My professional experience in the academic environment of the JHU/SOM Department
%of Biomedical Engineering has involved each of the listed requirements
%above, particularly with respect to the Research Associate faculty position
%that I held from 2019--2022~\see{job1}. The summaries above starting with
%\cfonly{basicreqs} provide additional context, and the linked sections indicated
%next to the arrows under each requirement provide further supporting details.


%\subsection*{Requirements for the GS-14 Level}

%\begin{itemize}
  %\item \emph{At least one year of professional experience that demonstrates
      %extensive scientific expertise incorporating research experience with
      %varied responsibilities for providing leadership in a scientific area, and
      %functioning as a leader for a variety of efforts, such as directing research
      %and coordinating committee and teaching activities, and organizing and
    %chairing sessions at national scientific meetings.}
  %\item \emph{Served as an appointed member of a scientific peer-review panel
    %or editorial board.} \itemnote{\cf{programsvc}.}
  %\item \emph{Held the position of Associate Professor, Professor or
      %equivalent.} \itemnote{\cf{cv} and also my note under the last listed
      %requirement for the GS-13 level above.}
%\end{itemize}

%I have three years of professional experience as a Research Associate~\see{job1}
%and five years of experience as a Postdoctoral Fellow~\see{job2} in which
%I employed my extensive research experience-based scientific expertise
%to undertake responsibilities for my independently developed portfolio
%of leadership efforts in computational and theoretical neuroscience and
%related subfields of control theory, autonomous systems, embodied cognition,
%and artificial intelligence. While these leadership efforts have been
%described above in response to other duties and requirements, they are
%also detailed in \cfonly{res}, \cfonly{service}, \cfonly{talks},
%\cfonly{presentations}, \cfonly{eduprogram}, and \cfonly{mentoring}. Recognition
%of these efforts---including \emph{Fast Company} magazine ranking JHUAPL as the
%\#3 ``Best Workplace for Innovators'' based on my NSF project---is detailed
%under \cfonly{recognition}.

%Selected examples of my research-based scientific leadership efforts include:
%%
%\begin{itemize}
  %\item Directed research conducted by my student mentees~\see{mentoring}
    %and key personnel or co-investigators on my funded research
    %projects~\see{res}.
  %\item Delivered invited research-based talks at national and international
    %scientific meetings and organizations~\see{natltalks}, e.g., AFRL (Sept 2022),
    %University of Toronto (Feb 2022), NIH BRAIN Investigators Meeting (June 2020),
    %JHU Kavli Neuroscience Discovery Institute (Oct 2019).
  %\item Contributed talks presenting novel theoretical integration of scientific
    %findings to international scientific/educational meetings~\see{intltalks}, e.g.,
    %Neuromatch Conference 3.0 (Oct 2020) and 4.0 (Dec 2021).
  %\item Served on the Review Committee for the Cosyne conference (2016, 2020,
    %2021)~\see{confsvc}.
  %\item Provided scientific peer-review for top computational neuroscience,
    %biology, and artificial intelligence journals including Neuron, eLife, PLOS
    %Computational Biology, Nature Machine Intelligence, and Neural Computation
    %(with the honorific of `Communicator', reserved for highly impactful peer
    %reviewers)~\see{service}.
  %\item Invited to provide inputs to guide programmatic development of DARPA/MTO
    %MEC (Jan 2022).
  %\item Invited and served as a reviewer on multiple NSF panels and as an ad-hoc
    %reviewer to evaluate funding applications according to scientific merit and
    %programmatic criteria (2021--2022)~\see{programsvc}.
  %\item Provided feedback to the NSF to help establish criteria and standards
    %for logistical discussion plans for panels with difficult multidisciplinary,
    %multiday workloads (April 2022).
  %\item Invited and participated in the NSF Workshop on Present and Future
    %Frameworks for Theoretical Neuroscience (Feb 2019)~\see{natltalks} and
    %contributed to a working-group preprint on the role of theory in neuroscience
    %(Levenstein, et al. 2020)~\see{preprints} that is currently under review at
    %the Journal of Neuroscience~\see{pubs}.
  %\item Proposed and co-organized national scientific and educational symposia,
    %e.g., at the NIH BRAIN Investigators Meeting (June 2020)~\see{natltalks} and
    %as part of the JHUAPL STEM Academy Program funded by my collaborative NSF
    %project (Jan 2021)~\see{eduprogram}.
  %\item Across the foregoing efforts, I have sought to convey overarching
    %guidance on emerging directions and caveats regarding methods, approaches, and
    %questions for neuroscience and related subfields.
%\end{itemize}


%%% HSA Self-Assessment Questionnaire --- Supporting Details}

\pagebreak
\newsection{Self-Assessment Questionnaire --- Supporting Details}{questionnaire}
\setlist{itemsep=1pt}

\begin{enumerate}
  \item I qualify for this position because I have completed all requirements
    for and successfully obtained a Ph.D. in Neurobiology \& Behavior from Columbia
    University in 2009.
  \item I confirm that I meet the basic experience requirements for all grades.
  \item Qualifying experience is described above under \cfonly{basicreqs}.
  \item I obtained a Ph.D. in Neurobiology \& Behavior from Columbia University
    in 2009.
  \item My qualifying experience occurred in an Academic Environment,
    as described above under \cfonly{basicreqs} and detailed below under
    \cfonly{workexp} with respect to my roles as a Research Associate,
    Postdoctoral Fellow, and Graduate Research Assistant at R1 research
    universities including Brandeis, Columbia, and Johns Hopkins.
  \item \emph{ibid.}
  \item \emph{ibid.}
  \item Job duties, related skills, and responsibilities for the listed
    qualifying positions are listed in detail within the corresponding
    position-related sections starting under \cfonly{workexp}.
  \item Listed areas of scientific expertise span my training, publications, and
    awarded grants as described above under \cfonly{basicreqs} and detailed below
    under \cfonly{workexp} and \cfonly{pubs}.
  \item My Ph.D. was granted by the Department of Neurobiology \& Behavior at
    Columbia University, where I conducted my doctoral studies as a Graduate
    Research Assistant in the Center for Theoretical Neuroscience as described
    under \cfonly{education}.
\end{enumerate}

For assessment items 11--37, supporting details for each skill or capability are
provided in the notes below the corresponding item.

\begin{enumerate}
  \setcounter{enumi}{10}
  \item Analyze the scientific merit of current and projected research programs. 
    \itemnote{Extramural contributor to development of funding programs at IARPA
    and the NSF~\see{programsvc}.}
  \item Analyze trends and new scientific fields to assess the adequacy of
    research being conducted and proposed in a given area.
    \itemnote{My education was grounded in mathematics and
      philosophy~\see{education}, which has allowed me to build methods that I use
      in my research from scratch and to assess their inferential utility, e.g.,
      with respect to statistical validity, etc. As I developed my independent
      research program~\see{res}, I gained substantial experience
      evaluating current trends in methods, approaches, and scientific questions
    in current and emerging fields.}
  \item Identify and recommend the program direction of new research.
    \itemnote{In nearly 23 years of experience in neuroscience
      research~\see{education}~\see{pubs}~\see{res}, I have developed deep
      intuitions and agility in recognizing and evaluating new lines of research.
      This interdisciplinary research experience has trained me to recognize
      critical distinctions between approaches that support useful recommendations
    on the potential strengths of new research.}
  \item Identify gaps in scientific research.
    \itemnote{As described for the previous two items, my interdisciplinary
      research and long history in neuroscience~\see{education}~\see{pubs} and
      related fields has informed my ability to assess the current state of the
      science. In particular, my theoretical interests inform how I survey for
    epistemic gaps based on processes of inductive reasoning.}
  \item Manage the development of organizational or research group policies in
    response to changes in levels of funding or legislative/program changes.
    \itemnote{Based on my extended history of interactions with program officers
      as described above in \cfonly{duties} and \cfonly{basicreqs}, I have extensive
      familiarity with organizational policies and requirements at funding agencies in
    response to funding level changes due to legislation or other factors.}
  \item Monitor scientific progress of research or clinical programs to assure
    that objectives are met.
    \itemnote{Given my experience, particularly as JHU/SOM Research
      Associate~\see{job1}, I have had to continually monitor scientific
      progress in internally and externally funded research projects at varied
      levels of budget and scope, e.g., for small team projects like my JHU/SLI
    award~\see{sligrant} and larger projects like my NSF award~\see{nsfgrant}.}
  \item Provide guidance or interpret regulations and funding policies regarding
    biomedical, behavioral health, or health-related research.
    \itemnote{As described above under \cfonly{duties}, my extensive
      interactions with program officers and federal funding agencies has deeply
      informed my ability to assess and interpret policy effects for health-releated
    research.}
  \item To verify your level of experience for the previous seven (7) questions,
    please list the name, email address, and phone number of someone who we can
    contact to get more information.
    \itemnote{Prof. Knierim was my postdoctoral supervisor from
      2009--2014~\see{job3}, and he is familiar and up-to-date with my current
    levels of experience and expertise.}
  \item Administer unsolicited grant/contract proposals and provide support
    regarding funding options and areas of program emphasis.
    \itemnote{As described above under \cfonly{duties} and below under
      \cfonly{programsvc}, my extensive interactions with program officers and my
      service on merit-review panels has given me substantial knowledge about the
      processes involved in unsolicited proposals and has informed my ability to
    support funding options aligned with program priorities.}
  \item Appoint and manage grants, contracts, or cooperative agreements review
    panels.
    \itemnote{My participation on multiple federal merit-review
      panels~\see{programsvc} and intensive interaction with BRAIN program staff
      over the last two years in my current role as a Scientific Program Manager
      for the NIH BRAIN Initiative~\see{jobobd} has given me substantial training
      in grants administration processes related to the logistics of appointing
      panels for these purposes.}
    \item Evaluate the technical and scientific merit of funding applications and
      proposals being submitted for approval.
      \itemnote{My extensive background in health-related research and
        scientific review based in the highly multidisciplinary field of
        neuroscience~\see{education}~\see{res}~\see{service} has provided me
        world-class preparation for evaluating the technical and scientific merit of
      funding applications.}
    \item Review applications for funding created by others to ensure
      they have been prepared properly. \itemnote{Reviewing NIH grant
        applications for correctness has been a core responsibility of my
        subject matter expert (SME) duties in my current role~\see{jobobd}
        over the last two years. Before joining the NIH, I prepared numerous
        funding applications and grant proposals intended for various funding
        agencies~\see{funding}~\see{res}, which has given me substantial
        real-world experience and knowledge regarding the proper preparation of
      funding applications.} 
    \item Recommend and distribute research funding for new research
      initiatives/efforts.
      \itemnote{My knowledge and familiarity with the processes of recommending
        and distributing research funding derive from my experience in my current
        role~\see{jobobd} interacting with program officers and BRAIN Teams as
      funding payplans are developed through the Council cycle.~\see{funding}.}
    \item Manage research fund distribution amongst competing interests within an
      organization.
      \itemnote{\emph{ibid.}}
    \item Obtain independent grant funding for research from either the private or
      public sector.
      \itemnote{I have successfully obtained independent research funding from
        public sector agencies~\see{funding} and have submitted several applications to
    private foundations.}
  \item Write or co-write research grants.
    \itemnote{I have extensive experience writing varied forms of grant
    proposals and funding applications. \cf{res}.}
  \item Have you ever served as a Program/Project Officer responsible for
    developing, coordinating, and administering grants, cooperative agreements and
    contracts?
    \itemnote{I have not served as a Program Officer, but I have worked closely
      with Program Officers across the 10 BRAIN-participating ICs in the last two
      years in my current role~\see{jobobd}. At the NIH, I have taken core curriculum
    training courses for Program Officers.}
  \item Deliver presentations to senior medical/health practitioners,
    professional societies, and academia on pertinent matters relating to
    biomedical, behavioral health, or clinical health-related research.
    \itemnote{As described above under \cfonly{duties} and \cfonly{basicreqs},
      I have extensive experience in scientific communication in many settings to
      varied audiences including professional, academic, and educational groups.
    \cfcf{talks}{presentations}.}
  \item Prepare major components of position papers or reviews on policy or
    critical scientific issues related to biomedical, behavioral health, or clinical
    health-related research.
    \itemnote{I have written original research articles across the extent of my
      career, and I have more recently taken to writing higher-level perspective-style
      review papers that give broader views of critical scientific problems and
      questions. My extensive writing experience will translate to preparation of
      position papers, policy reviews, etc., related to scientific or health-related
    issues. \cfcf{pubs}{preprints}.}
  \item Present briefings on research to high level officials providing multiple
    alternatives and advice on the best course of action.
    \itemnote{See notes for items \#17, \#19, \#28, and \#29 above.}
  \item Write reports, evaluations, summary statements, or correspondences as a
    part of a review process.
    \itemnote{As described in the notes for items \#21, \#22, and \#29 and
      my experience writing summary statements on review panels~\see{programsvc},
      I have extensive knowledge, experience, and skill in evaluating proposals
      within a review process and in writing clearly about scientific, technical, and
      health-related topics. These skills will translate to the writing of reports and
    summary statements.}
  \item Coach and mentor staff engaged in biomedical, behavioral health, or
    clinical health-related research.
    \itemnote{\cf{mentoring}.}
  \item Create project plans, including project scope, goals, tasks, resources,
    schedules, costs, contingencies, and communications.
    \itemnote{\cf{res}.}
  \item Manage and direct multiple research or project teams concurrently.
    \itemnote{In the narrative summaries provided above under \cfonly{duties}
      and \cfonly{basicreqs}, the activities that I described occurred
    concurrently or overlapping in time.}
  \item Manage research or project execution to ensure adherence to budget,
    schedule, and scope.
    \itemnote{I have extensive experience managing and co-managing projects of
      varied scale, from small teams to large cross-divisional collaborations,
    including scheduling, budget, and scope of work. \cf{res}.}
  \item Monitor the performance of research or project team members, providing,
    and documenting technical feedback.
    \itemnote{As noted for item \#35, my experience in research project
      management also extends to interacting usefully with team members by listening
      to them, monitoring their progress, and providing constructive and helpful
    feedback at appropriate times.}
  \item Resolve conflicts, differences, or problems among colleagues,
    subordinates, or team members.
    \itemnote{I have worked to resolve conflicts and differences in approach
      between team members in extramural program environments and in research
    projects of various size and scope. \cfcf{res}{mentoring}.}
\end{enumerate}

 
%%% Work Experience %%%

\pagebreak
\input{workexp}


%%% Professional and Academic References --- Contact Info %%%

\pagebreak
\newsection{Professional \& Academic References}{references}
\input{../../jobsearch/references/references_nih}


%%% CURRICULUM VITAE --- SUPPORTING INFORMATION %%%

\pagebreak
\newsection{Curriculum Vitae --- Supporting Information}{cv}
\input{header}


%%% Educational History %%%

\input{education}


%%% Publications %%%

\renewcommand{\itemnote}[1]{}
%
\input{pubs}


%%% Funding Award History %%%

\smallskip
\input{funding}
%
\renewcommand{\itemnote}[1]{
  \begin{description}
    \item[$\rightarrow$] \hspace{.09in}{\color{darkgray}\it #1}
  \end{description}
}


%%% Professional Service --- Peer Review & Programmatic Contributions %%%

\smallskip
\input{service}


%%% Professional and Scientific Presentations %%% 

\smallskip
\input{presentations}


%%% Recognition and Coverage of My Work %%%

\smallskip
\input{recognition}


%%% Communications & Media %%%

\smallskip
\input{comms_media}


%%% Research Program Development %%%

\medskip
\input{research_development}


%%% Educational Activities %%%

\medskip
\pagebreak
\input{teaching}


\end{document}
