%!TEX root = cv.tex

\newsection{Professional \& Scientific Presentations}{talks}

\subsection*{International}
\vspace{-0.1in}
\label{sec:intltalks}

\begin{longtable}{@{\hspace{0.0in}}l>{\raggedright\arraybackslash}p{.82\textwidth}}
  12/14/2024 & \href{https://neurips.cc/virtual/2024/workshop/84721}
  {``\itemtitle{Looking forward from the BRAIN workshop to a transformative
    future for NeuroAI}.'' \emph{Invited Speaker}. NeuroAI Workshop, NeurIPS (Neural
  Information Processing Systems) 2024 Conference, Vancouver, BC, Canada}
  [\href{https://neurips.cc/virtual/2024/84817}{\unpubtitle{SlidesLive}}] \\
  \tabularnewline
  11/12--13/2024 \hspace{0.1in} & \href{https://braininitiative.nih.gov/news-events/events/brain-neuroai-workshop}
  {``\itemtitle{Introduction to the Workshop: Gaps, Questions, and
    Opportunities}.'' \emph{Organizer, Speaker, Moderator}. BRAIN NeuroAI Workshop,
  NIH Main Campus, Bethesda, MD (Hybrid).}
  [\href{https://videocast.nih.gov/watch=55160}{\unpubtitle{VideoCast Day 1}} \&
  \href{https://videocast.nih.gov/watch=55262}{\unpubtitle{Day 2}}] 
  [\href{https://braininitiative.nih.gov/sites/default/files/documents/BRAIN%20NeuroAI%20Workshop%20Summary_2024_508c.pdf}{\unpubtitle{Meeting Summary}}] \\
  \tabularnewline
  10/5/2024 & \href{https://www.sfn.org/meetings/neuroscience-2024/sessions-and-events/professional-development-workshops#Saturday,-October-05}
  {``\itemtitle{The NIH BRAIN Initiative: Working with AI in Neuroscience}.''
    \emph{Invited Speaker, Panelist}. Society for Neuroscience 2024, Professional
    Development Workshop on ``\unpubtitle{Working With and Working For AI}'',
  Chicago, IL} \\
  \tabularnewline
  9/25/2024 & \href{https://neuroinformatics.incf.org/2024/sessions}{``\itemtitle{The
    present and future of the BRAIN data ecosystem for neuroscience and beyond}.''
    \emph{Co-Organizer, Speaker, Panelist}. INCF (International Neuroinformatics
    Coordinating Facility) Assembly. {Panel on \unpubtitle{\emph{BRAIN
          Initiative Informatics Perspectives: Funding and Building a Sustainable Data
  Ecosystem}}}, Austin, TX} \\
  \tabularnewline
  7/31/2024 & \href{https://iconsneuromorphic.cc/schedule/}
  {\unpubtitle{Discussion Panel on Neuromorphic Systems and U.S. Government}.
  \emph{Invited Speaker, Panelist}. IEEE/ACM ICONS (International Conference on 
Neuromorphic Systems) 2024, George Mason University, Arlington, VA } \\
  \tabularnewline
  7/12/2024 &
  \href{https://sites.google.com/view/telluride-2024/home}{``\itemtitle{Coordination 
      dynamics of behavior and cognitive computation: Rethinking emergent control}.'' 
      \emph{Invited Talk}. Telluride Neuromorphic Workshop 2024, Telluride, CO}.
    [\href{https://youtu.be/7b69GXB2jBc?si=xuzXOZDqXWl6I_sO}{\unpubtitle{YouTube}}] \\
  \tabularnewline
  10/13/2023 & \href{https://jdmonaco.com/files/monaco-IAPCT-2023-slides.pdf}
    {``\itemtitle{Cognitive-narrative dynamics of self-perspective control
    across the lifespan}.''} \emph{Invited Talk}. 33rd Annual International
    Association for Perceptual Control Theory (IAPCT) Conference, 
  \href{https://www.iapct.org/uncategorized/utc-4-boston-time-zone/}
  {Session 7 on \unpubtitle{\emph{Consciousness and the Self}}}, Virtual
  [\href{https://jdmonaco.com/files/monaco-IAPCT-2023-slides.pdf}{\unpubtitle{pdf}}] \\
  \tabularnewline
  10/12/2023 & \href{https://odin.mit.edu/schedule.html}
    {``\itemtitle{Beyond ‘FAIR’: What does sustainable protocolization of
    open data in neuroscience look like?}'' \emph{Invited Panelist, Keynote
    Speaker}. Open Data in Neuroscience (ODIN) Symposium, Massachusetts Institute
  of Technology, Boston, MA} \\
  \tabularnewline
  3/8/2023 & \href{https://meetings.aps.org/Meeting/MAR23/Session/M01.13}
  {``\itemtitle{Neurodynamical computing at the information boundaries of
    intelligent systems}.'' \emph{Contributed Talk}. American Physical Society (APS)
  March Meeting, Las Vegas, NV}
  [\href{https://jdmonaco.com/files/monaco-APS-March-Meeting-2023-slides.pdf}{\unpubtitle{pdf}}] \\
  \tabularnewline
  2/1/2022 & ``\unpubtitle{Theory-Driven Data Science to
  Understand the Neural Dynamics of Memory and Behavior}.'' \emph{Invited Talk}.
  Department of Cell \& Systems Biology, University of Toronto, Canada, Virtual \\
  \tabularnewline
  %12/1/2021 & ``\unpubtitle{Learning as swarming: Cognitive
  %flexibility from the neural dynamics of phase-coupled attractor maps}.''
  %\emph{Contributed Talk}. Neuromatch 4.0 Conference, Virtual \\
  %\tabularnewline
  12/1/2021 & \href{https://youtu.be/3mKkLksOyfk}{``\itemtitle{Learning as
  swarming: Cognitive flexibility from the neural dynamics of phase-coupled
  attractor maps}.'' \emph{Contributed Talk}. Neuromatch 4.0 Conference,
  Virtual \itemtitle{[YouTube]}} \\
  \tabularnewline
  %10/29/2020 & ``\unpubtitle{Spatial theta-phase coding in
  %the lateral septum: A theory of allocentric feedback during navigation}.''
  %\emph{Contributed Talk}. Neuromatch 3.0 Conference, Virtual \\
  %\tabularnewline
  10/29/2020 & \href{https://www.youtube.com/watch?v=WwYDMpD7j4Q}{``\itemtitle{Spatial
  theta-phase coding in the lateral septum: A theory of allocentric feedback
  during navigation}.'' \emph{Contributed Talk}. Neuromatch 3.0 Conference,
  Virtual \itemtitle{[YouTube]}} \\
  \tabularnewline
  10/7/2020 & ``\unpubtitle{Computing path integration with
  oscillatory phase codes in biological and artificial systems}.'' \emph{Data
  Blitz}. iNAV Symposium 2020, Virtual \\
  \tabularnewline
  7/1/2010 & ``\unpubtitle{Medial versus lateral modes for
  reconfiguring hippocampal representations}.'' \emph{Invited Talk}. Grid
  Cell Meeting, Gatsby Computational Neuroscience Unit, UCL, UK \\
\end{longtable}


\subsection*{National}
\label{sec:natltalks}
\vspace{-0.1in}

\begin{longtable}{@{\hspace{0.1in}}l>{\raggedright\arraybackslash}p{.82\textwidth}}
  8/28/2024 & \href{https://www.aim-ahead.net/webinar-series/ai-cares/}
  {``\itemtitle{The NIH BRAIN Initiative: AI in Neuroscience}.'' \emph{Invited
  Talk}. AI-CARES (AI Career Advancement and Resources) Webinar Series,
  AIM-AHEAD, Virtual}
  %Webinar Series, AIM-AHEAD (Artificial Intelligence/Machine Learning Consortium
  %to Advance Health Equity and Researcher Diversity), Virtual}
  [\href{https://www.aim-ahead.net/media/u3bmfrsa/ai-cares-dr-monaco.pdf}{\unpubtitle{pdf}}] \\
  \tabularnewline
  8/21/2024 & \href{https://braininitiative.nih.gov/sites/default/files/documents/BRAIN%20NEWG_Agenda_Aug%202024%20v8_508C.pdf}
    {``\itemtitle{Introduction and Overview of AI, Neuroscience, and Ethics}.''
      \emph{Co-Organizer, Speaker}. BRAIN Neuroethics Working Group (NEWG)
    Workshop, NIH/NINDS, Virtual} 
    [\href{https://videocast.nih.gov/watch=54989}{\unpubtitle{VideoCast}}] \\
  \tabularnewline
  6/18/2024 & \href{https://brainmeeting.swoogo.com/2024/agenda#Wednesday}
  {``\itemtitle{Specialty Session: BRAIN and the Future of Computing: Emerging
    Perspectives on Embodied NeuroAI Research}.'' \emph{Co-Organizer, Moderator}.
  10th Annual BRAIN Initiative Conference, Rockville, MD} 
  [\href{https://youtu.be/3W0o0Mmc60o?si=ejmzy70NFG0jAOp_}{\unpubtitle{YouTube}}] \\
  \tabularnewline
  9/26--28/2023 & BRAIN Initiative Cell Atlas Network (BICAN)
  Knowledge Base Workshop. \emph{BRAIN Liaison \& Invited Participant}. Allen
  Institute for Brain Sciences, Seattle, WA \\
  \tabularnewline
  7/17--18/2023 \hspace{0.1in} &
  \href{https://event.roseliassociates.com/brain-newg-ws-july-2023/}
  {\itemtitle{Workshop on Ethics of Sharing Individual Level Human Brain
    Data Collected in Biomedical Research}. \emph{Co-Organizer, Breakout
    Moderator/Reporter}. BRAIN Initiative Neuroethics Working Group (NEWG), NIH,
  Bethesda, MD (Hybrid)} \\
  \tabularnewline
  5/9/2023 & 
  \href{https://jdmonaco.com/files/monaco_TheoryOfTheory_slides.pdf}
  {``\itemtitle{Theory of theory: On the role of
  theory and modeling in neuroscience}.'' \emph{Invited Extramural Seminar}.
  NIH, Virtual [\unpubtitle{pdf}]} \\
  \tabularnewline
  4/28/2023 & 
  \href{https://jdmonaco.com/files/monaco-2023-afrl-quest-slides.pdf}
  {``\itemtitle{Neurodynamical Articulation: Decoupling Intelligence from the
  Experiencing Self}.'' \emph{Invited Public Seminar}. QuEST, Air Force Research
  Lab/Autonomous Capabilities Team 3 (AFRL/ACT3), Virtual [\unpubtitle{pdf}]} \\
  \tabularnewline
  12/21/2022 & ``\unpubtitle{Finding Causal Paths Across Scales:
  Embodied Control, Ethological Interaction, and Theory-Driven Neural Data
  Science}.'' \emph{Invited Talk}. Division of Neuroscience and Behavior,
  NIH/NIDA, Virtual \\
  \tabularnewline
  11/17/2022 & ``\unpubtitle{Finding Causal Paths Across Scales:
  Embodied Control, Ethological Interaction, and Theory-Driven Neural Data
  Science}.'' \emph{Invited Talk}. Division of Neuroscience and Basic Behavioral
  Science, NIH/NIMH, Virtual \\
  \tabularnewline
  8/26/2022 &
  \href{https://jdmonaco.com/files/monaco-2022-afrl-quest-slides.pdf}
  {``\itemtitle{Brain oscillations: From cortical computing to the existential
  nonduality of conscious agents}.'' \emph{Invited Public Seminar}. Qualia
  Exploitation for Sensor Technology (QuEST), Air Force Research Lab/Autonomous
  Capabilities Team 3 (AFRL/ACT3), Virtual [\unpubtitle{pdf}]}\\
  \tabularnewline
  6/1/2020 & \href{https://youtu.be/2jy1ENYHRAw?t=902}
  {``\itemtitle{Can Transitory Neurodynamics Unify Learning Theories for Brains
  and Machines?}'' \emph{Invited Talk \& Panel Discussion}.}
  6th Annual BRAIN Initiative Investigators Meeting,
  \href{https://www.labroots.com/webinar/symposium-1-dynamical-systems-neuroscience-reciprocally-advance-machine-learning} 
  {Symposium 1 on \unpubtitle{\emph{How Can Dynamical Systems Neuroscience
  Reciprocally Advance Machine Learning?}}}, NIH, Virtual 
  [\href{https://youtu.be/2jy1ENYHRAw?t=902}{{\itemtitle{YouTube}}}] \\
  \label{sec:symposium}
  \tabularnewline
  5/18/2020 & ``\unpubtitle{Computational Approaches to the
  Neural Dynamics of Time, Memory, and Behavior}.'' \emph{Invited Talk}.
  Department of Neuroscience, Medical Discovery Team for Optical Imaging,
  University of Minnesota, Virtual \\
  \tabularnewline
  2/24/2020 & ``\unpubtitle{Computational Mechanisms of Memory:
  Linking Behavior, Space, \& Time}.'' \emph{Invited Talk}. Department of
  Psychology, University of Nevada, Las Vegas, NV \\
  \tabularnewline
  1/31/2020 & ``\unpubtitle{Attractors, memory, and oscillations:
  Computational motifs of spatial learning}.'' \emph{Invited Talk}.
  Department of Biological Sciences, University of Texas at El Paso, El Paso, TX \\
  \tabularnewline
  4/17/2019 & ``\unpubtitle{Emergent dynamics of hippocampal
  circuitry as a basis for robust self-organized planning in mobile swarms}.''
  \emph{Invited Talk}. International Society for Optics and Photonics (SPIE)
  Defense \& Commercial Sensing 2019 Conference, Baltimore, MD \\
  \tabularnewline
  4/10/2019 & NSF/Neural \& Cognitive Systems (NCS) PI
  Workshop. \emph{Invited Participant}. Marriott Wardman Park Hotel, Washington, D.C. \\
  \tabularnewline
  2/3--7/2019 \hspace{0.1in} & NSF/BRAIN Initiative Workshop: Present and Future Frameworks
  of Theoretical Neuroscience. \emph{Invited Participant}. University of Texas,
  San Antonio, TX \\
  \tabularnewline
  1/3/2014 & \href{https://jdmonaco.com/files/ScanningSlide.pdf}
  {``\itemtitle{Head scans drive the formation and potentiation of place
  fields during exploration}.'' \emph{Data Blitz}. 38th Winter Conference on
  Neurobiology of Learning \& Memory, Park City, UT} \\
  \tabularnewline
  4/10/2009 & ``\unpubtitle{Rapid spatial map formation and remapping by
  competing over grid cell inputs}.'' \emph{Thesis Seminar}. Department of
  Neurobiology \& Behavior, Columbia University, New York, NY 
  [\href{https://jdmonaco.com/files/monaco-2009-thesis-seminar-Keynote.mp4}
  {\unpubtitle{Keynote Movie Export (mp4)}}] \\
\end{longtable}

\subsection*{Regional}
\vspace{-0.1in}

\begin{longtable}{@{\hspace{0.2in}}l>{\raggedright\arraybackslash}p{.82\textwidth}}
  10/2/2019 \hspace{0.1in} & ``\unpubtitle{Oscillations, attractors, and
  sequences: Extending hippocampal computations to artificial systems}.''
  \emph{Invited Talk}. Kavli Neuroscience Discovery Institute, Johns Hopkins
  University, Baltimore, MD\\
  \tabularnewline
  1/22/2016 & ``\unpubtitle{Hippocampal circuits for space, memory, and
  navigation: From minimal models to biologically inferred networks}.''
  \emph{Invited Talk}. Department of Pharmacology, University of Maryland,
  Baltimore, MD\\
  \tabularnewline
  9/6/2014 & ``\unpubtitle{Stopping to look: How attentive scanning behavior
  reveals the formation of new memories}.'' \emph{Department Retreat Seminar}.
  Department of Neuroscience, Johns Hopkins University, Baltimore, MD\\
  \tabularnewline
  4/21/2014 & ``\unpubtitle{Landmark influence: How attention to sensory cues
  stabilizes and updates the hippocampal cognitive representation of space}.''
  \emph{Advanced Researcher Seminar}. Zanvyl Krieger Mind/Brain Institute, Johns
  Hopkins University, Baltimore, MD\\
  \tabularnewline
  4/1/2014 & ``\unpubtitle{Hippocampus and declarative memory:
  Head scanning}.'' \emph{Department `Lab Lunch' Seminar}. Department of
  Neuroscience, Johns Hopkins University, Baltimore, MD\\
\end{longtable}


\smallskip
\subsection*{Research Poster Presentations}
\label{sec:presentations}
\vspace{-0.1in}

\begin{description}[itemsep=8pt]
  \item[\quad]
    \href{https://www.cvent.com/events/6th-annual-brain-initiative-investigators-meeting/custom-116-4e2aadaa6cd549a3a4b53113cd172ad2.aspx}
    {\joehl{Monaco JD}, Hwang GM, Schultz K, Zhang K. (2020).
    \itemtitle{Cognitive swarming in complex environments with attractor
        dynamics and oscillatory computing}. \emph{6th Annual BRAIN Initiative
    Investigators Meeting}. Online, with audio narration. June~2020.}
  \item[\quad]
    \href{https://www.fens.org/Meetings/The-Brain-Conferences/Dynamics-of-the-brain/}
    {\joehl{Monaco JD}, Hwang GM, De Guzman RM, Blair HT, Zhang K. (2019).
    \itemtitle{Spatial rate-phase coding in lateral septal ‘phaser cells’:
        single-unit data and theta-bursting models}. \emph{FENS (Federation of
        European Neuroscience Societies) Dynamics of the brain: Temporal aspects of
    computation}. North Copenhagen, Denmark. June~2019.}
  \item[\quad]
    \href{https://www.cvent.com/events/5th-annual-brain-initiative-investigators-meeting/event-summary-de9c0d8f934b46eb8d80b55bcfbfe96a.aspx}
    {\joehl{Monaco JD}, Hwang GM, Schultz K, Zhang K. (2019).
    \itemtitle{Self-organized swarm control using neural principles of spatial
      phase coding}. \emph{5th Annual BRAIN Initiative Investigators Meeting}.
    Washington, D.C. April~2019.} 
  \item[\quad]
    \href{https://abstractsonline.com/pp8/#!/4649/presentation/10884}
    {Hwang GM, Schultz K, \joehl{Monaco JD}, Chalmers RW, Lau SW, Yeh BY,
      Zhang K. (2018). \itemtitle{Self-organized swarm control using neural
      principles of spatial phase coding}. \emph{Society for Neuroscience}.
    San Diego, CA. November~2018.}
  \item[\quad]
    \href{https://www.abstractsonline.com/pp8/#!/4376/presentation/6085}
    {\joehl{Monaco J}, Blair HT, Zhang K. (2017). \itemtitle{Decoding
        septohippocampal theta cells during exploration reveals unbiased
      environmental cues in firing phase}. \emph{Society for Neuroscience}.
    Washington, D.C. November~2017.}
  \item[\quad]
    \href{https://jdmonaco.com/files/monaco-paper-cosyne15.pdf}
    {\joehl{Monaco JD}, Blair HT, Zhang K. (2015). \itemtitle{Spatial
        rate/phase correlations in theta cells can stabilize randomly drifting path
    integrators}. \emph{Cosyne}. Salt Lake City, UT. March~2015.}
  \item[\quad]
    \href{https://www.abstractsonline.com/Plan/ViewAbstract.aspx?sKey=973d2662-ba7a-4ad2-aff9-fe0d4b77c262&cKey=9917ffaf-9e31-4213-acb9-4aab498ab4cd&mKey=54c85d94-6d69-4b09-afaa-502c0e680ca7}
    {\joehl{Monaco J}, Blair HT, Zhang K. (2014). \itemtitle{Spatial rate/phase
        codes provide landmark-based error correction in a temporal model of theta
    cells}. \emph{Society for Neuroscience}. Washington, D.C.  November~2014.}
  \item[\quad]
    \href{https://www.abstractsonline.com/Plan/ViewAbstract.aspx?sKey=bfb59866-8deb-44a6-9515-a7aab630507b&cKey=d201b3aa-7725-452e-b0dd-c41d204b5b54&mKey=54c85d94-6d69-4b09-afaa-502c0e680ca7}
    {Wang CH, Rao G, \joehl{Monaco JD}, Deshmukh SS, Knierim JJ. (2014).
    \itemtitle{Potentiation of place fields along the CA1 transverse axis by
      investigatory head-scanning behavior}. \emph{Society for Neuroscience}. 
    Washington, D.C. November~2014.}
  \item[\quad]
    \href{https://www.abstractsonline.com/Plan/ViewAbstract.aspx?sKey=32eccac1-4e1d-4e81-bf5c-f39bcb605757&cKey=4710dece-cc8e-4b48-8764-49ea174b91ef&mKey=8d2a5bec-4825-4cd6-9439-b42bb151d1cf}
    {\joehl{Monaco J}, Rao G, Knierim JJ. (2013). \itemtitle{Scanning behavior
        in novel environments promotes \emph{de novo} formation of hippocampal place
    fields in rats}. \emph{Society for Neuroscience}. San Diego, CA. November~2013.}
  \item[\quad]
    \href{https://www.abstractsonline.com/Plan/ViewAbstract.aspx?sKey=f5b9fa94-7d15-48c7-9d67-b89cd2883025&cKey=a53349ca-41b1-4664-b022-85d0d1fe59b8&mKey=70007181-01C9-4DE9-A0A2-EEBFA14CD9F1}
    {\joehl{Monaco J}, Rao G, Knierim JJ. (2012). \itemtitle{Hippocampal LFP
      during rodent head-scanning behavior: Theta and sharp-wave ripples}.
    \emph{Society for Neuroscience}. New Orleans, LA. October~2012.}
  \item[\quad]
    \href{https://www.abstractsonline.com/Plan/ViewAbstract.aspx?sKey=c48e9f5f-1274-4486-85bf-38ee591629e1&cKey=190bd951-c183-428d-a4c5-01eb61556d79&mKey=8334BE29-8911-4991-8C31-32B32DD5E6C8}
    {\joehl{Monaco J}, Rao G, Knierim JJ. (2011). \itemtitle{Hippocampal place
        cell firing during head-scanning movements is associated with the formation
    of new place fields}. \emph{Society for Neuroscience}. Washington, D.C. November~2011.}
  \item[\quad]
    \href{https://www.abstractsonline.com/Plan/ViewAbstract.aspx?sKey=c48e9f5f-1274-4486-85bf-38ee591629e1&cKey=3ec26e6f-8c59-4be2-bad3-e1572d75e07e&mKey=8334BE29-8911-4991-8C31-32B32DD5E6C8}
    {Rao G, \joehl{Monaco J}, Knierim JJ. (2011). \itemtitle{Environmental
        novelty promotes rodent head-scanning behavior linked to enhanced entorhinal
      activity}. \emph{Society for Neuroscience}. Washington,
    D.C. November~2011.}
  \item[\quad]
    \href{https://www.frontiersin.org/10.3389/conf.fnins.2010.03.00192/event_abstract}
    {\joehl{Monaco JD}, Zhang K, Blair HT, Knierim JJ. (2010).
    \itemtitle{Cue-based feedback enables remapping in a multiple oscillator
      model of place cell activity}. \emph{Cosyne}. Salt Lake City, UT.
    February~2010.}
  \item[\quad] \joehl{Monaco JD}, Abbott LF. (2009). \unpubtitle{Dynamic
      hippocampal remapping using recurrent inhibition on realigning grid cell
    inputs}. \emph{Cosyne}. Salt Lake City, UT. February~2009.
  \item[\quad] \joehl{Monaco JD}, Muzzio IA, Levita L, Abbott LF. (2006).
    \unpubtitle{Entorhinal input and global remapping of hippocampal place
    fields}. \emph{CNS}. Edinburgh, UK. July~2006.
  \item[\quad] \joehl{Monaco JD}, Abbott LF. (2006). \unpubtitle{Entorhinal
    input and the remapping of hippocampal place fields}. \emph{Cosyne}. Salt Lake
    City, UT. March~2006.
  \item[\quad] \joehl{Monaco JD}, Levy WB. (2003). \unpubtitle{T-maze training
      of a recurrent CA3 model reveals the necessity of novelty-based modulation of
    LTP in hippocampal region CA3}. \emph{IJCNN}. Portland, OR. July~2003.
  \item[\quad] \joehl{Monaco JD}, Perlstein RP. (1997). \unpubtitle{Monte-Carlo
      analysis of deoxyhypusine synthase inhibitor ligand conformations}. \emph{NIH
    Poster Day}. Bethesda, MD. August~1997.
\end{description}

