%!TEX root = cv.tex
\section*{Journal Publications}

\begin{description}
  \item Hadzic A, Hwang GM, Zhang K, Schultz KM, and \joehl{Monaco JD}.
    (\emph{\color{lightred}In revision}). \itemtitle{Bayesian optimization of
    distributed neurodynamical controller models for spatial navigation}.
    \emph{Array}.
  \item \joehl{Monaco JD}, Rajan K, and Hwang GM. (\emph{\color{lightred}In revision}).
      \itemtitle{A brain basis of dynamical intelligence for AI and computational
    neuroscience}. \emph{Nature Machine Intelligence}.
  \item \href{https://dx.doi.org/10.1007/s00422-020-00823-z}
    {\joehl{Monaco JD}, Hwang GM, Schultz KM, and Zhang K. (2020).
    \itemtitle{Cognitive swarming in complex environments with attractor
      dynamics and oscillatory computing}. \emph{Biological Cybernetics}, 114,
    269--284. \doi{10.1007/s00422-020-00823-z}}
  \item \begin{samepage}\href{https://dx.doi.org/10.1016/j.cub.2020.01.083} 
      {Wang CH, \joehl{Monaco JD}, and Knierim JJ. (2020). \itemtitle{Hippocampal
        place cells encode local surface texture boundaries}. \emph{Current Biology},
      30, 1--13. \doi{10.1016/j.cub.2020.01.083}}
  \itemnote{I mentored the first author in data analysis of rat behavior and
      single-unit recordings, developed the software toolchain used to conduct the
    analyses, and provided intellectual guidance.}\end{samepage}
  \item \href{https://dx.doi.org/10.1371/journal.pcbi.1006741}
    {\joehl{Monaco JD}, De Guzman RM, Blair HT, and Zhang K. (2019).
    \itemtitle{Spatial synchronization codes from coupled rate-phase
      neurons}. \emph{PLOS Computational Biology}, 15(1), e1006741.
    \doi{10.1371/journal.pcbi.1006741}}
  \item \href{https://www.cell.com/cell/fulltext/S0092-8674(18)31228-5}
    {Tabuchi M, \joehl{Monaco JD}, Duan G, Bell BJ, Liu S, Zhang K, and
      Wu MN. (2018). \itemtitle{Clock-generated temporal codes determine
      synaptic plasticity to control sleep}. \emph{Cell}, 175(5), 1213--27.
    \doi{10.1016/j.cell.2018.09.016}}
  \itemnote{I developed two modeling strategies for the Wu lab’s circadian clock
      neuron experiments in \emph{Drosophila}. My generative statistical model was
      integrated into stimulation protocols as a timing control for behavioral
      results, and my mechanistic molecular/neuronal model explained observed trends
      and made predictions corroborated by the data. My results or contributions are
    featured in 3/7 main figures and 3/6 supplementary figures.}
  \item \href{https://dx.doi.org/10.1038/nn.3687}
    {\joehl{Monaco JD}, Rao G, Roth ED, and Knierim JJ. (2014).
    \itemtitle{Attentive scanning behavior drives one-trial potentiation of
      hippocampal place fields}. \emph{Nature Neuroscience}, 17(5), 725--731.
    \doi{10.1038/nn.3687}}
  \itemnote{\href{https://jdmonaco.com/files/monaco-2014-author-manuscript.pdf}{
    Click here for author manuscript as accepted.}}
  \itemnote{\href{https://jdmonaco.com/files/monaco-2014-suppinfo.pdf}{
    Click here for supplementary information with figures and analysis diagrams.}}
  \item \href{https://dx.doi.org/10.3389/fncom.2011.00039}
    {\joehl{Monaco JD}, Knierim JJ, and Zhang K. (2011). \itemtitle{Sensory
        feedback, error correction, and remapping in a multiple oscillator model of
      place cell activity}. \emph{Frontiers in Computational Neuroscience}, 5:39.
    \doi{10.3389/fncom.2011.00039}}
  \item \href{https://dx.doi.org/10.1523/JNEUROSCI.1433-11.2011}
    {\joehl{Monaco JD} and Abbott LF. (2011). \itemtitle{Modular
        realignment of entorhinal grid cell activity as a basis for hippocampal
      remapping}. \emph{Journal of Neuroscience}, 31(25), 9414--25.
    \doi{10.1523/jneurosci.1433-11.2011}}
  \item \href{https://dx.doi.org/10.1371/journal.pbio.1000140}
    {Muzzio IA, Levita L, Kulkarni J, \joehl{Monaco J}, Kentros CG, Stead
      M, Abbott LF, and Kandel ER. (2009). \itemtitle{Attention enhances the
        retrieval and stability of visuospatial and olfactory representations
      in the dorsal hippocampus}. \emph{PLOS Biology}, 7(6), e1000140.
    \doi{10.1371/journal.pbio.1000140}}
  \itemnote{I contributed oscillatory power analyses and group-level statistical
      analyses of spiking and bursting for odor vs.\ visuospatial tasks in
    single-unit hippocampal recordings from freely-moving mice.}
  \item \href{https://dx.doi.org/10.1101/lm.363207}
    {\joehl{Monaco JD}, Abbott LF, and Kahana MJ. (2007).
    \itemtitle{Lexico-semantic structure and the recognition
      word-frequency effect}. \emph{Learning \& Memory}, 14(3), 204--213.
    \doi{10.1101/lm.363207}}
\end{description}

\section*{Conference Papers}

\begin{description}
  \item Buckley E, \joehl{Monaco JD}, Schultz KM, Chalmers R, Hadzic A, Zhang
      K, Hwang GM, and Carr MD. (2021). \itemtitle{An interdisciplinary approach
      to high school curriculum development: Swarming Powered by Neuroscience}.
      \emph{Proceedings of the 12th IEEE Integrated STEM Education Conference
    (ISEC)}. Accepted.
  \item \href{https://www.jhuapl.edu/Content/techdigest/pdf/V35-N04/35-04-Hwang.pdf}
    {Hwang GM, Schultz KM, \joehl{Monaco JD}, and Zhang K. (2021).
    \itemtitle{Neuro-Inspired Dynamic Replanning in Swarms—Theoretical
        Neuroscience Extends Swarming in Complex Environments}. \emph{Johns Hopkins
    APL Technical Digest}, 35, 443--447.}
  \item \href{https://dx.doi.org/10.1117/12.2518966}
    {\joehl{Monaco JD}, Hwang GM, Schultz KM, and Zhang K. (2019).
    \itemtitle{Cognitive swarming: An approach from the theoretical neuroscience
        of hippocampal function}. \emph{Proceedings of SPIE (International society
      for optics and photonics) Defense \& Commercial Sensing}. Micro- and
      Nanotechnology Sensors, Systems, and Applications XI, 109822D, 1--10.
    \doi{10.1117/12.2518966}}
  \item \href{https://dx.doi.org/10.1109/IJCNN.2003.1223655}
    {\joehl{Monaco JD} and Levy WB. (2003). \itemtitle{T-maze training
        of a recurrent CA3 model reveals the necessity of novelty-based
        modulation of LTP in hippocampal region CA3}. \emph{Proceedings of
      International Joint Conference on Neural Networks}, 1655--1660.
    \doi{10.1109/IJCNN.2003.1223655}}
  \itemnote{This paper received First Place in the IJCNN Student Paper
    Competition.}
  \itemnote{\href{https://jdmonaco.com/files/monaco-2003-tmaze.pdf}{Click here
    for author manuscript as accepted.}}
\end{description}

\section*{Preprints}

\begin{description}
  \item \href{https://arxiv.org/abs/2111.00599}{Hadzic A, Hwang GM, Zhang K,
      Schultz KM, and \joehl{Monaco JD}. (2021). \itemtitle{Bayesian optimization
      of distributed neurodynamical controller models for spatial navigation}.
    \arxiv{2111.00599}}
  \item \href{https://arxiv.org/abs/2109.05545}{Buckley E, \joehl{Monaco JD},
      Schultz KM, Chalmers R, Hadzic A, Zhang K, Hwang GM, and Carr MD. (2021).
    \itemtitle{An interdisciplinary approach to high school curriculum development:
    Swarming Powered by Neuroscience}. \arxiv{2109.05545}}
  \item \href{https://arxiv.org/abs/2105.07284}
    {\joehl{Monaco JD}, Rajan K, and Hwang GM. (2021). \itemtitle{A brain
      basis of dynamical intelligence for AI and computational neuroscience}.
    \arxiv{2105.07284}}
  \item \href{https://arxiv.org/abs/2003.13825}
    {Levenstein D, Alvarez VA, Amarasingham A, Azab H, Gerkin RC, Hasenstaub
      A, Iyer R, Jolivet RB, Marzen~S, \joehl{Monaco JD}, Prinz AA, Quraishi
      S, Santamaria F, Shivkumar S, Singh MF, Stockton DB, Traub R, Rotstein
      HG, Nadim F, and Redish AD. (2020). \itemtitle{On the role of theory and
    modeling in neuroscience}. \arxiv{2003.13825}}
  \item \href{https://arxiv.org/abs/1909.06711}
    {\joehl{Monaco JD}, Hwang GM, Schultz KM, and Zhang K. (2019).
    \itemtitle{Cognitive swarming in complex environments with attractor
    dynamics and oscillatory computing}. \arxiv{1909.06711}}
  \item \href{https://dx.doi.org/10.1101/764282}
    {Wang CH, \joehl{Monaco JD}, and Knierim JJ. (2019). \itemtitle{Hippocampal
      place cells encode local surface texture boundaries}. \emph{bioRxiv}.
    \doi{10.1101/764282}}
  \item \href{https://dx.doi.org/10.1101/211458}
    {\joehl{Monaco JD}, Blair HT, and Zhang K. (2017). \itemtitle{Spatial theta
        cells in competitive burst synchronization networks: Reference frames from
    phase codes}. \emph{bioRxiv}. \doi{10.1101/211458}}
\end{description}

\section*{Thesis}

\begin{description}
  \item \href{https://search.proquest.com/docview/304862872/abstract}
    {\joehl{Monaco JD}. (2009). \itemtitle{Models and mechanisms for integrating
      cortical feature spaces}. Doctoral Dissertation, Columbia University, New
    York. \emph{ProQuest Publication No. AAT 3393609}}
  \itemnote{\href{https://jdmonaco.com/files/monaco-phdthesis-2009.pdf}{Click
    here for submitted version with high-quality color figures.}}
\end{description}

