%!TEX root = cv.tex

\newsection{Recognition \& Coverage of My Work}{recognition}

\subsection*{Awards \& Honors}
\label{sec:awards}
\vspace{-0.1in}

\lefttabline{0.8in}{2024}{Kelly Government Services, Distinguished Achievement Award}
\lefttabline{0.8in}{2022}{IEEE/ISEC Best Paper Award, First Place}
\lefttabline{0.8in}{2003}{IEEE/IJCNN Student Paper Award, First Place}
\lefttabline{0.8in}{2002}{U.Va. John A. Harrison III Undergraduate Research Award}
\lefttabline{0.8in}{1999--2003}{U.Va. Echols Scholar}
\lefttabline{0.8in}{1999}{State of Maryland Merit Scholastic Award}
\lefttabline{0.8in}{1999}{AP Scholar with Distinction}
\lefttabline{0.8in}{1999}{National Merit Scholarship Commended Student}
\lefttabline{0.8in}{1999}{Johns Hopkins Mathematics Competition (2nd Place, Individual Calculus)}
\lefttabline{0.8in}{1999}{Maryland Distinguished Scholar}

\subsection*{News \& Views}
\vspace{-0.1in}

\begin{itemize}[itemsep=6pt]
  \item \href{https://dx.doi.org/10.1016/j.cub.2020.02.085}
    {Place R, Nitz DA. (2020). \itemtitle{Cognitive Maps: Distortions of the Hippocampal 
      Space Map Define Neighborhoods}. \emph{Current Biology}, 30(8): R340--R342.}
  \item \href{https://dx.doi.org/10.1016/j.cell.2018.10.047}
    {Colwell CS, Donlea J. (2018). \itemtitle{Temporal coding of sleep}. \emph{Cell}, 175(5): 1177--9.}
  \item \href{https://dx.doi.org/10.1038/nn.3700}
    {Dupret D, Csicsvari J. (2014). \itemtitle{Turning heads to remember
    places}. \emph{Nature Neuroscience}, 17(5): 643--44.}
\end{itemize}

\subsection*{Post-Publication Reviews}
\vspace{-0.1in}

\begin{itemize}[itemsep=6pt]
  \item \href{https://facultyopinions.com/prime/718333676#eval793494783}
    {Moser E, Rowland D. (May 12, 2014). ``\itemtitle{This exciting study finds
        an unexpected relationship between exploratory head scanning behavior
      and the development of new place fields in the rat hippocampus...}”
    \emph{F1000/Faculty Opinions}.}
  \item \href{https://facultyopinions.com/prime/718333676#eval793493493}
    {Maler L. (April 10, 2014). ``\itemtitle{This elegant and original study has
        demonstrated a strong link between the neural activity of hippocampal pyramidal
        neurons (PNs) during head scanning behavior and their subsequent acquisition of
    a new place field...}'' \emph{F1000/Faculty Opinions}.}
  \item \href{https://facultyopinions.com/prime/11553956}
    {Giocomo L, Moser E. (June 29, 2011) ``\itemtitle{This paper presents an
        interesting computational model which utilizes grid-cell modularity to generate
    robust remapping...}'' \emph{F1000/Faculty Opinions}.}
\end{itemize}

\subsection*{Other Press}
\label{sec:press}
\vspace{-0.1in}

\begin{itemize}[itemsep=6pt]
  \item \href{https://www.fastcompany.com/90529833/best-workplaces-for-innovators-2020 -johns-hopkins-university-apl} 
    {``\itemtitle{Johns Hopkins University APL is one of Fast Company’s Best Workplaces
      for Innovators}.'' (July 29, 2020). \emph{Fast Company}.
      \aurl{https://www.fastcompany.com/90529833/best-workplaces-for-innovators- 2020-johns-hopkins-university-apl}}
      \itemnote{My NSF project (see p.\pageref{sec:funding}) was the basis for
      \#3 ranking of JHUAPL.}
  \item \href{https://blogs.plos.org/biologue/2019/03/20/better-use-of-mouse-models-skin-infection-dynamics-and-phaser-cells-in-navigation/}
    {``\itemtitle{Better Use of Mouse Models, Skin Infection
      Dynamics, and Phaser Cells in Navigation}.'' (March 20,
      2019). \emph{PLOS Computational Biology: Biologue}.
      \aurl{https://blogs.plos.org/biologue/2019/03/20/ 
    better-use-of-mouse-models-skin-infection-dynamics-and-phaser-cells-in-navigation/}}
  \itemnote{Editor-in-Chief's selection of papers.}
  %\item \href{https://nationalsciencefoundation.tumblr.com/post/183448836933/brain-awareness-week-2019-rats-and-robots}
    %{``\itemtitle{Brain Awareness Week 2019—Rats and Robots: NSF-funded researchers
        %take a lesson from rat navigation instincts to improve algorithm[s] for
      %robots}.'' (March 14, 2019). \emph{National Science Foundation/Tumblr}.
    %\aurl{https://nationalsciencefoundation.tumblr.com/post/ 183448836933/brain-awareness-week-2019-rats-and-robots}}
  \item \href{https://www.medicaldaily.com/cognitive-map-can-show-real-time-when-memories-form-thanks-place-cells-brain-276790}
    {``\itemtitle{Cognitive Map Can Show In Real-Time When Memories Form, Thanks
      To Place Cells In The Brain}.'' (April 15, 2014). Chris Weller/Medical Daily.
    \aurl{https://www.medicaldaily.com/cognitive-map-can- show-real-time-when-memories-form-thanks-place-cells-brain-276790}}
\end{itemize}

