%!TEX root = cv.tex

\vbox{%
\newsection{Education Activities}{teaching}

\smallskip
\subsection*{Educational Program Development}
\vspace{-0.1in}
\label{sec:eduprogram}
}

\begin{tabular}{@{\hspace{0.2in}}l>{\raggedright\arraybackslash}p{.82\textwidth}}
  2018--2021 \hspace{0.1in} & My NSF project with JHUAPL (see \cfonly{funding}
  and \cfonly{nsfgrant}) was successfully funded with a substantial STEM
  component for high-school students involving the development of both a
  12-week course and an intense 2-day seminar called ``Swarming Powered by
  Neuroscience.'' I worked with our STEM education collaborators at JHUAPL to
  develop computational resources required for the two curricula. Additionally,
  I participated in and delivered two virtual lectures about our research
  for the 4-day STEM workshop (developed due to Covid requirements) with 40+
  students that was held Jan 2021.
\end{tabular}

\smallskip
\subsection*{Mentoring \& Supervision}
\label{sec:mentoring}
\vspace{-0.1in}

\begin{longtable}{@{\hspace{0.2in}}l>{\raggedright\arraybackslash}p{.82\textwidth}}
  Spring 2021 \hspace{0.05in} & Darius Carr, STEM high school student; I mentored
  Darius as part of a local high school program that facilitates research
  internships for underrepresented students. I developed a computational
  research project with him that deepened his current interests in neuroscience,
  python programming, and scientific research. \\
  \tabularnewline
  2020--2022 \hspace{0.1in} & Armin Hadzic, junior machine learning engineer
  at JHUAPL; I supervised Armin in translating computational neuroscience
  models into the domain of reinforcement learning and Bayesian optimization
  to investigate autonomous swarming with neural control. Our project led to
  a first author peer-reviewed research publication for Armin in Array (see
  \cfonly{hadzicpub}). In 2022, I provided letters of recommendation in
  support of Armin's applications to Ph.D. programs in computer science. \\
  \tabularnewline
  2019--2023 & Sreelakshmi Rajendrakumar, master's student in JHU/Biomedical
  Engineering (BME); I mentored Sreelakshmi in hippocampal physiology and
  single-unit data analysis. In 2023, I provided letters of recommendation in
  support of Sree's applications to Ph.D. programs in operations research and
  causal inference. \\
  \tabularnewline
  2014 & Manning Zhang, M.S., graduate student in JHU/BME; I mentored Manning
  through an exchange program with Shanghai Jiao Tong University and submitted
  a letter of recommendation supporting her admission to the JHU/BME master's
  program. \\
  \tabularnewline
  2013--2015 & Chia-Hsuan Wang, Ph.D., graduate student at the JHU/MBI; I worked
  extensively with Chia-Hsuan to take over my previous studies of behavior
  and place cells in the Knierim lab, leading to a Society for Neuroscience
  conference poster in 2014. I supported her subsequent thesis research based on
  my analytics and informatics software, resulting in a paper in Current Biology
  (see \cfonly{wangpub}). \\
\end{longtable}


\subsection*{Classroom Instruction}
\vspace{-0.1in}

\begin{tabular}{@{\hspace{0.2in}}l>{\raggedright\arraybackslash}p{.82\textwidth}}
  Fall 2004 & Teaching Assistant for undergraduate ``Introduction to
  Neuroscience'' course, Brandeis University; I assisted Prof. Eve Marder by
  supervising classes, grading examinations, and giving review lectures.\\
  \tabularnewline
  Spring 2005 \hspace{.1in} & Teaching Assistant for undergraduate ``Biology
  Laboratory'' course, Brandeis University \\
\end{tabular}

